Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-11 paper/main.tex
typo fix in intro
major code reorganization, started notebook for running stats
- working on results section - added Campbell as an author (yay!)

\author{Jeremy R. Manning\textsuperscript{1, *}, Kirsten
Ziman\textsuperscript{1, 2}, Emily Whitaker\textsuperscript{1},\\Paxton C.
Fitzpatrick\textsuperscript{1}, Madeline R. Lee\textsuperscript{1}, 
Allison M Frantz\textsuperscript{1}, \\Bryan J.
Bollinger\textsuperscript{1}, and Andrew C. Heusser\textsuperscript{1,
3}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Princeton
University\\\textsuperscript{3}Akili
Interactive\\\textsuperscript{*}Corresponding author:
jeremy.r.manning@dartmouth.edu}

@@

Experience is subjective: different people who encounter identical physical
experiences can take away very different meanings and memories. One reason is
that our subjective experiences in the moment are shaped in part the
idiosyncratic prior experiences, memories, goals, thoughts, expectations, and
emotions that we bring with us into the present moment. These factors
collectively define a \textit{context} for our experiences~\citep{Mann20}. %
situation models: forming expectations, predicting ambiguous future experiences
The contexts we encounter help us to construct \textit{situation
models}~\citep{RangRitc12, MannEtal15} or \textit{schemas}~\citep{MasiEtal22,
BaldEtal18} that describe how experiences are likely to unfold based on our
prior experiences with similar contextual cues. For example, when we enter a
sit-down restaurant, we might expect to be seated at a table, given a menu, and
served food. Priming someone to expect a particular situation or context can
also influence how they resolve potentail ambiguities in their ongoing
experiences, including ambiguous movies and narratives~\citep{YeshEtal17}.

@@

>>>>

\author{Jeremy R. Manning\textsuperscript{1, *}, Kirsten
Ziman\textsuperscript{1, 2}, Emily Whitaker\textsuperscript{1},\\Paxton C.
Fitzpatrick\textsuperscript{1}, Madeline R. Lee\textsuperscript{1}, Allison M
Frantz\textsuperscript{1},\\Bryan J. Bollinger\textsuperscript{1}, Campbell E.
Field\textsuperscript{1}, and Andrew C. Heusser\textsuperscript{1,
3}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Princeton
University\\\textsuperscript{3}Akili
Interactive\\\textsuperscript{*}Corresponding author:
jeremy.r.manning@dartmouth.edu}

@@

Experience is subjective: different people who encounter identical physical
experiences can take away very different meanings and memories. One reason is
that our subjective experiences in the moment are shaped in part the
idiosyncratic prior experiences, memories, goals, thoughts, expectations, and
emotions that we bring with us into the present moment. These factors
collectively define a \textit{context} for our experiences~\citep{Mann20}.

% situation models: forming expectations, predicting ambiguous future experiences

The contexts we encounter help us to construct \textit{situation
models}~\citep{RangRitc12, MannEtal15} or \textit{schemas}~\citep{MasiEtal22,
BaldEtal18} that describe how experiences are likely to unfold based on our
prior experiences with similar contextual cues. For example, when we enter a
sit-down restaurant, we might expect to be seated at a table, given a menu, and
served food. Priming someone to expect a particular situation or context can
also influence how they resolve potentail ambiguities in their ongoing
experiences, including ambiguous movies and narratives~\citep{YeshEtal17}.

@@

We sought to manipulate two aspects of how participants memorized sequences of
word lists. First, we added two additional sources of visual variation to the
individual word presentations: font color and onscreen location. Importantly,
these visual features were independent of the meaning or semantic content of
the words (e.g., word category, size of the refferent) and of the lexicographic
properties of the word (e.g., word length, first letter). We wondered whether
this additional word-independent information might facilitate recall (e.g., by
providing new potential ways of organizing or retrieving memories of the
studied words) or impair recall (e.g., by distracting participants). Second,
our primary experimental manipulations entailed manipulating the orders in
which words were studied (and how those orderings changed over time). We
wondered whether presenting the same list of words in different orders (e.g.,
sorted along one feature dimension versus another) might serve to influence how
participants organized their memories of the words. We also wondered whether
some order manipulations might be temporally ``sticky'' by influencing how
\textit{future} lists were remembered.
